Paper 1

### 2018-09-12 paper1.tex
Shortened solution to the 1st proof.
Added a proof for theorem 5

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	From the AM-GM inequality, we know
	\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
	\end{align*}
	Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
	\begin{align*}
	\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
	\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
	\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
	\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
	\end{align*}
	We know that all terms are positive in the above inequality, so,
	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
	This implies that 
	$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

@@

	Next, we will show that the following equation also holds for the described sequences:
	$$a_n^2-2b_n^2 = (-1)^n.$$
	When $n=1$,
	\begin{align*}
	\mbox{LHS} = a_1^2-2b_1^2=1-2=-1\\	
	\mbox{RHS} = (-1)^1=-1{2}.
	\end{align*}
	So $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1.$
	Now, assume that the equation holds for a particular natural number $n$.
	We want to show that the equation must also hold for $n+1$.
	Now, consider
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= (a_n+2b_n)^2-2(b_n+a_n)^2\\
		&= a_n^2 + 4b_na_n +4b^2_n - 2(b_n^2+2a_nb_n+a_n^2)\\
		&= 2b_n^2-a^2_n\\
		&= -1(a^2_n-2b_n^2).
	\end{align*}
	We know from our induction hypothesis that $a_n^2-2b_n^2 = (-1)^n$, so
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= -1(-1)^n \\
		a_{n+1}^2-2b_{n+1}^2 &= (-1)^{n+1}.
	\end{align*}
	Therefore, the equation holds for $n+1$, if it holds for a natural number $n$. By induction on $n$, the equation holds for all natural number $n$.

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
	% Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
	% Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

>>>>

\begin{proof}[Correct proof of theorem~\ref{thm:mean-spirited}]
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Use the AM-GM inequality.
	%
	\begin{comment} %My initial longer solution
		From the AM-GM inequality, we know
		\begin{align*}
		\frac{a+b+c}{3} \geq \sqrt[3]{abc}. 
		\end{align*}
		Because we know $abc$ is a positive number, $\sqrt[3]{abc}$ is also positive. So, we can perform the following,
		\begin{align*}
		\frac{(a+b+c)(\sqrt[3]{abc})^2}{3} &\geq abc \\
		\frac{(a+b+c)}{(abc)^{\frac{1}{3}}} &\geq 3 \\
		\frac{(a)^{\frac{2}{3}}}{(bc)^{\frac{1}{3}}} + \frac{(b)^{\frac{2}{3}}}{(ac)^{\frac{1}{3}}} + \frac{(c)^{\frac{2}{3}}}{(ab)^{\frac{1}{3}}}&\geq 3 \\
		\sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}&\geq 3
		\end{align*}
		We know that all terms are positive in the above inequality, so,
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq \sqrt[3]{\frac{a^2}{bc}}+\sqrt[3]{\frac{b^2}{ac}}+\sqrt[3]{\frac{c^2}{ab}}\geq3.$$
		This implies that 
		$$ \frac{a^2}{bc} + \frac{b^2}{ac} + \frac{c^2}{ac} \geq 3 .$$
	\end{comment}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From the AM-GM inequality, we know
	\begin{align*}
		\frac{a^3+b^3+c^3}{3} &\geq \sqrt[3]{a^3b^3c^3} \\
		{a^3+b^3+c^3} &\geq 3abc.
	\end{align*}
	Since we know that $a,b,c > 0$,
	\begin{align*}
		\frac{a^3+b^3+c^3}{abc} &\geq 3 \\
		\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} &\geq 3.
	\end{align*}
\end{proof}

@@

	Next, we will show that the following equation also holds for the described sequences:
	$$a_n^2-2b_n^2 = (-1)^n.$$
	When $n=1$,
	\begin{align*}
	\mbox{LHS} = a_1^2-2b_1^2=1-2=-1\\	
	\mbox{RHS} = (-1)^1=-1.
	\end{align*}
	So $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1.$
	Now, assume that the equation holds for a particular natural number $n$.
	We want to show that the equation must also hold for $n+1$.
	Now, consider
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= (a_n+2b_n)^2-2(b_n+a_n)^2\\
		&= a_n^2 + 4b_na_n +4b^2_n - 2(b_n^2+2a_nb_n+a_n^2)\\
		&= 2b_n^2-a^2_n\\
		&= -1(a^2_n-2b_n^2).
	\end{align*}
	We know from our induction hypothesis that $a_n^2-2b_n^2 = (-1)^n$, so
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= -1(-1)^n \\
		a_{n+1}^2-2b_{n+1}^2 &= (-1)^{n+1}.
	\end{align*}
	Therefore, the equation holds for $n+1$, if it holds for a natural number $n$. By induction on $n$, the equation holds for all natural number $n$.

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	 %The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
	 %Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
	 %Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
	%
	For a contradiction, let us assume that $1+\sqrt{2}$ is rootional. This means that there exists natural power of $1+\sqrt{2}$ that is equal to a rational number.  So, we can write
	$$ \left(1+\sqrt{2}\right)^n = \frac{c}{d} $$
	for natural number $n$ and integers $c,d$. From Lemma 4, we know that \\
	$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}$, so substituting this into the earlier equation yields
	\begin{align*}
		a_n + b_n \sqrt{2} &= \frac{c}{d} \\
		\sqrt{2} &= \frac{\frac{c}{d}-a_n}{b_n} \\
		\sqrt{2} &= \frac{c-a_nd}{b_nd}
	\end{align*}
	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$, an integer. 
	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a fraction of two integers, which is rational. So the RHS is rational, but we know that $\sqrt{2}$, which is the LHS, is irrational.

	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}
